\noindent Dear Sean O'Meara, \\

\noindent I am writing to express interested in working for your company over my summer break (December - March) as an Software Developer which is part of an internship. \\

\noindent ImPOS particularly interested me because of one of the job ads you posted on Seek sometime ago, it mentioned what your team was like to work with
and the technologies that you were using. After speaking further to Carissa Babb at Geared Asset Finance, I was really impressed by what she said about your team - thinking I would fit in perfectly and as I result I could not help but put forward my resumè. \\

\noindent One of the other reasons I would like an internship at ImPOS is solve real world problems whilst using version control, automated builds/testing, etc,.
I believe am not sufficiently exposed to these at University and would like to use them on a much larger, professional scale. \\

\noindent I have had a great deal of experience with programming in a wide variety of languages from both University and personal interest.
These range from shell scripting to mobile development. \\

\noindent I believe I would be an asset to your team because of my enthusiasm, drive and general love for solving problems. \\

\noindent In support of my application I have attached a resume providing a more detailed summary of my relevant experiences. I look forward to discussing my application
further at an interview.

\vspace{10 mm}

\noindent Yours Faithfully \\

\noindent Dale Salter
