\documentclass[10pt]{scrartcl}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern} % load a font with all the characters


\renewcommand{\familydefault}{\sfdefault}
\usepackage{helvet}

% The title details
\title{ImPos}
\subtitle{Cover Letter}
\author{Dale Salter}
\date{\today}

% Header

\begin{document}
\pagenumbering{gobble} % Remove page numbers (and reset to 1)

\maketitle

% Content
\noindent Dear Sean O'Meara, \\

\noindent I am writing to express interested in working for your company over my summer break (December - March) as an Software Developer which is part of an internship. \\

\noindent ImPos particularly interested me because of one of the job ads you posted on Seek sometime ago, it mentioned what your team was like to work with
            and the technologies you were using. After speaking further to Carissa Babb at Geared Asset Finance, I was really impressed by what she said about your team and could not help but put forward my resumè. \\

\noindent I have had a great deal of experience with programming in a wide variety of languages from both University and personal interest.
            These range from shell scripting to mobile development. \\

\noindent The reason I would like an internship is because I would like to work with team on real world problems whilst using version control, automated builds/testing, etc,.
            This is because I believe am not sufficiently exposed to these at University and would like to use them on a larger more professional scale. \\

\noindent I believe I would be an asset to your team because of my enthusiasm, drive and just general love for solving problems. \\

\noindent In support of my application I have attached a resume providing a more detailed summary of my relevant experiences and projects. I look forward to discussing my application
            further at interview.

\vspace{10 mm}

\noindent Yours Faithfully \\

\noindent Dale Salter

\end{document}
